\thispagestyle{empty}

\centerline{\Large{\textbf{Acknowledgements}}}

\vspace{2cm}

\noindent 
First and foremost, I would like to express my sincere gratitude to Prof.~Dr.~Christian Bauckhage for his continuous support during this thesis. He has not only been my supervisor but also a very inspirational figure during my Master's studies. This is my heartfelt thanks for his motivational lectures which have helped me to improve as a computer science student and pursue the field of machine learning. \\\\
I would also like to offer my gratitude to Prof.~Dr.~Stephan Wrobel for supervising this thesis. His work in the field of machine learning has always been an inspiration for me.\\\\
To my life coach, my grandfather, and my father, I would like to dedicate all that I have achieved till date because they are the reason for what I am today. I look up to them as they never stop giving their hundred percent even when things get difficult and inspire me to do the same. I would also acknowledge my mom and my siblings for always having my back. I would also like to acknowledge my gratitude to Mr. Ankit Gupta, co-founder Pulse, who not only has motivated me to challenge myself daily but also inspired me to do my best.\\\\
I also extend my gratitude towards Mr.Sven Giesselbach and Dr.Tim Witz for being very understanding and supporting during my thesis completion. Last but not least, I am grateful towards my friends who have always supported me during these months.


\newpage
\thispagestyle{empty}

\rule{0cm}{5cm}